Git Learning Notes

### 2014-08-01 ch-intro/ch-instr.tex
moo3 draft 50%

The synthesis was accomplished in a home-made hot-wall CVD system, as visualized in Fig.~\ref{fig:ch2cvd}. The furnace is made by two semi-cylindrical ceramic fiber heaters (WATLOW inc.) with power density from 0.8 to 4.6 \si{W cm^{-2}}. Quartz tube (Quartz Sci inc.) of 1 inch diameter was primarily used as reaction chamber. A mechanical pump was connected to maintain the low pressure environment inside the chamber. The length of uniform heating zone is 6 inches, with cooling zone extending outward. Carriers gas argon (Ar) and reactant gas oxygen (\ce{O2}) was regulated by two mass flow controllers.

@@

\begin{table}[htb]
\centering
\caption{CVD parameters map}\label{tab:cvd}
    \begin{tabular}{lcccr}
    \toprule
     &&&\multicolumn{2}{c}{Flow} \\
    \cmidrule(l){4-5}
             & Temperature & Pressure & Ar & \ce{O2}  \\
    \midrule
             & \si{\degreeCelsius} & mTorr & sccm & sccm\\
    \midrule
    Range      & RT-1100    & 10mTorr-1atm & 0 - 100 & 0-30  \\
    Resolution & $\pm1$  & correlated to flow & 1   & 0.1  \\
    \bottomrule
    \end{tabular}
\end{table}

@@

\item Acceleration voltage: 10 kV
\item Working distance: 10 mm
\item Scanning time: 80 sec
\end{itemize}
\item EDX
\begin{itemize}

@@

Crystal structures of the as-synthesized specimens in this study were characterized using PANXpert X’pert Pro MRD with Cu $K\alpha_{avg}$ radiation at $\lambda$=1.5418\AA. The nanostructures in this work usually grew without preferred orientation, and can be treated as powders. So the $\theta-2\theta$ configuration was primarily used, as shown in Fig.~\ref{fig:ch2theta}.

@@

\begin{table}[htb]
\centering
\caption{Scattering angle difference of Si(111)}\label{tab:ch2tem}
\begin{tabular}{lccr}
\toprule
Si(111) spacing & Source & Wavelength & scattering angle($2\theta$) \\
\midrule
3.135\AA & Cu $K\alpha$ & 1.541\AA & 28.45$^\circ$  \\
3.135\AA & 200 kV & 0.0251\AA \textsuperscript{\emph{a}}& 0.45$^\circ$  \\
\bottomrule
\end{tabular}

@@

Raman spectroscopy, a common vibrational spectroscopy, is based on the inelastic scattering of a monochromatic excitation source in energy range of 100 to 4000 $cm^{-1}$. Being nondestructive and requiring minimal preparation, 
it is an excellent tools to assess lattice dynamics and fingerprint species.\cite{McCreery2000}

In this study, Raman measurement was performed using a confocal micro-Raman system (Horiba Scentific, Labram HR800) with excitation wavelengths of 441, 532 and 632 nm. For nanowire samples, the laser powers were kept between 0.2 and 0.3 mW, and the acquisition time was 100 sec to avoid possible thermal damage. The spectral resolution is about 1 $cm^{-1}$ and the depth resolution about $2\mu m$.

@@

UV-Vis-NIR spectrophotometer is also a useful tool to obtain absorption and reflectance from various samples. The absorption can be described by Lambert-Beer law: $I = I_0 \exp{-\alpha(\lambda) x}$, where $\alpha$ is the absorption coefficient in unit of $cm^{-1}$, and $x$ is the optical path. When the sample is in liquid form, it is more convenient to use $I = I_0 \exp{-\epsilon(\lambda) C x}$, where $C(M = mol dm^{-3})$ is the molar concentration, and $\epsilon (M^{-1}cm^{-1})$ is the extinction coefficient. For example, $\epsilon$ for methylene blue (MB) is $10^5 M^{-1}cm^{-1}$ at 660 nm.\cite{Mills1999}

In this thesis, optical absorption spectra was recorded using Schimadzu, UV2600Plus in transmission mode. When necessary, the as-synthesized sample was removed from substrates by light sonication(Branson 1510R-MTH, 70W) in ethanol or DI water for 15 seconds. The dispersion was left for 12 hrs to enable the possible sedimentation. Then the dispersion was transferred into one 10 mm quartz cuvette (Thorlabs, W005654) for absorption measurement with another paired cuvette containing pairing liquid only.

\section{Substrates and Pre-growth Treatments}

Silicon and silicon dioxides on Si wafer ($p$-Si(100),Unversity Wafer inc.) were primarily used, and other substrates (i.e. Mica\footnote{ \ce{K(Al2)(Si3Al)O10(OH)2}}, glass (Fisher Scientific, microscope slide, 12-549),\footnote{Typical composition is 72.6\% \ce{SiO2}, 0.8\% \ce{B2O3}, 1.7\% \ce{Al2O3}, 4.6\% \ce{CaO}, 3.6\% \ce{MgO} and 15.2\% \ce{Na2O}} stainless steel) were occasionally adapted. Substrates were first cut into rectangular pieces of certain size and then ultrasonically cleaned (Branson 1510R-MTH) with acetone and alcohol for about 15 minutes each followed by blow-drying with nitrogen gas. After solution cleaning, the Si surface is hydrophobic. Depending on the specific experimental requirement, sometimes a hydrophilic surface is desired. We use plasma cleaning (Kurt J Lesker: Plasma-Preen 862) under 2 Torr \ce{O2} for 3 min to render a hydrophilic Si surface. In addition, substrates can be coated with a thin layer of metal before growth. This process will be covered  in Sec.~\ref{sec:mag}.

>>>>

The synthesis was accomplished in a home-made hot-wall CVD system, as visualized in Fig.~\ref{fig:ch2cvd}. The furnace is made by two semi-cylindrical ceramic fiber heaters (WATLOW inc.) with power density from 0.8 to 4.6 \si{W cm^{-2}}. Quartz tube (Quartz Sci inc.) of 1 in diameter was primarily used as reaction chamber. A mechanical pump was connected to maintain the low pressure environment inside the chamber. The length of uniform heating zone is 6 in, with cooling zone extending outward. Carriers gas argon (Ar) and reactant gas oxygen (\ce{O2}) was regulated by two mass flow controllers.

@@

\begin{table}[htb]
\centering
\caption{CVD parameters map}\label{tab:cvd}
    \begin{tabular}{lcccr}
    \toprule
     &&&\multicolumn{2}{c}{Flow} \\
    \cmidrule(l){4-5}
             & Temperature & Pressure & Ar & \ce{O2}  \\
    \midrule
             & \si{\degreeCelsius} & mTorr & sccm & sccm\\
    \midrule
    Range      & RT-1100    & 10 mTorr-1 atm & 0 - 100 & 0-30  \\
    Resolution & $\pm1$  & correlated to flow & 1   & 0.1  \\
    \bottomrule
    \end{tabular}
\end{table}

@@

\item Acceleration voltage: 10 kV
\item Working distance: 10 mm
\item Scanning time: 80 s
\end{itemize}
\item EDX
\begin{itemize}

@@

Crystal structures of the as-synthesized specimens in this study were characterized using PANXpert X’pert Pro MRD with Cu $K\alpha_{avg}$ radiation at $\lambda$=1.5418 \AA. The nanostructures in this work usually grew without preferred orientation, and can be treated as powders. So the $\theta-2\theta$ configuration was primarily used, as shown in Fig.~\ref{fig:ch2theta}.

@@

\begin{table}[htb]
\centering
\caption{Scattering angle difference of Si(111)}\label{tab:ch2tem}
\begin{tabular}{lccr}
\toprule
Si(111) spacing & Source & Wavelength & scattering angle($2\theta$) \\
\midrule
3.135 \AA & Cu $K\alpha$ & 1.541 \AA & 28.45$^\circ$  \\
3.135 \AA & 200 kV & 0.0251 \AA \textsuperscript{\emph{a}}& 0.45$^\circ$  \\
\bottomrule
\end{tabular}

@@

Raman spectroscopy, a common vibrational spectroscopy, is based on the inelastic scattering of a monochromatic excitation source in energy range of 100 to 4000 \si{cm^{-1}}. Being nondestructive and requiring minimal preparation, 
it is an excellent tools to assess lattice dynamics and fingerprint species.\cite{McCreery2000}

In this study, Raman measurement was performed using a confocal micro-Raman system (Horiba Scentific, Labram HR800) with excitation wavelengths of 441, 532 and 632 nm. For nanowire samples, the laser powers were kept between 0.2 and 0.3 mW, and the acquisition time was 100 s to avoid possible thermal damage. The spectral resolution is about 1 \si{cm^{-1}} and the depth resolution about $2 \mu m$.

@@

UV-Vis-NIR spectrophotometer is also a useful tool to obtain absorption and reflectance from various samples. The absorption can be described by Lambert-Beer law: $I = I_0 \exp{-\alpha(\lambda) x}$, where $\alpha$ is the absorption coefficient in unit of \si{cm^{-1}}, and $x$ is the optical path. When the sample is in liquid form, it is more convenient to use $I = I_0 \exp(-\epsilon_\lambda C x)$, where $C(M = mol dm^{-3})$ is the molar concentration, and $\epsilon (M^{-1}cm^{-1})$ is the extinction coefficient. For example, $\epsilon$ for methylene blue (MB) is $10^5 M^{-1}cm^{-1}$ at 660 nm.\cite{Mills1999}

In this thesis, optical absorption spectra was recorded using Schimadzu, UV2600Plus in transmission mode. When necessary, the as-synthesized sample was removed from substrates by light sonication(Branson 1510R-MTH, 70W) in ethanol or DI water for 15 seconds. The dispersion was left for 12 h to enable the possible sedimentation. Then the dispersion was transferred into one 10 mm quartz cuvette (Thorlabs, W005654) for absorption measurement with another paired cuvette containing pairing liquid only.

\section{Substrates and Pre-growth Treatments}\label{ch2sub}

Silicon and silicon dioxides on Si wafer ($p$-Si(100),Unversity Wafer inc.) were primarily used, and other substrates (i.e. Mica\footnote{ \ce{K(Al2)(Si3Al)O10(OH)2}}, glass (Fisher Scientific, microscope slide, 12-549),\footnote{Typical composition is 72.6\% \ce{SiO2}, 0.8\% \ce{B2O3}, 1.7\% \ce{Al2O3}, 4.6\% \ce{CaO}, 3.6\% \ce{MgO} and 15.2\% \ce{Na2O}} stainless steel) were occasionally adapted. Substrates were first cut into rectangular pieces of certain size and then ultrasonically cleaned (Branson 1510R-MTH) with acetone and alcohol for about 15 minutes each followed by blow-drying with nitrogen gas. After solution cleaning, the Si surface is hydrophobic. Depending on the specific experimental requirement, sometimes a hydrophilic surface is desired. A plasma cleaning was used (Kurt J Lesker: Plasma-Preen 862) to render a hydrophilic Si surface. The treatment was done at 2 Torr \ce{O2} for 3 minutes. In addition, substrates can be coated with a thin layer of metal before growth. This process will be covered  in Sec.~\ref{sec:mag}.

### 2014-08-01 ch-intro/ch-intro.tex
moo3 draft 50%

\chapter{introduction: nanomaterials for energy applications}

\section{Background and Motivation}

@@

@@

The materials studied in this work/dissertation are tungsten oxides (\ce{WO3}), molybdenum oxides (\ce{MoO3}),and their chalcogenide counterparts (\ce{WS2} and \ce{MoS2}). Both tungsten (W) and molybdenum (Mo) belong to Group VIB transition metal, with outer shell electrons configuration as $4d^55s^1$ and $5d^46s^2$ respectively. Therefore we refer their oxides and chalcogenides as \gls{tmo} and \gls{tmdc}.\footnote{Obviously transition metals include many other elements, all of which have partially filled $d$-electron shell. But here we use TM to denote W and Mo exclusively.} We have synthesized \gls{tmo} and \gls{tmdc} at nanoscale, measured their crystalline structures and optical properties and demonstrated some devices assembled using as-synthesized nanomaterials. We aim to illustrate that by nanoengineering these \gls{tmo} and \gls{tmdc}, enhanced performances over their bulk states could be expected and new properties will arise. In the remaining sections of this chapter, we will discuss some general perspectives of nanomaterials, the growth apparatus and characterization methods that apply to all experiments done in this work. Then chapter 2 will focus on growth of \ce{WO3} and its derivative. We employed thermal \gls{cvd} to synthesize \ce{WO3} \gls{nw}, and we investigated the role of impurity in tungsten metallic powders, during which we observed a new state of sodium tungsten oxides: \ce{Na5W14O44} nanowires. We also found a method to potentially obtain large yield of \ce{WO3} \gls{nw}. Chapter 3 will concentrate on \ce{MoO3}. We explored two different growth mechanism of \ce{MoO3}:\gls{vs} and \gls{vls}. We discovered that alkaline oxides can be used as catalyst to grow two distinct \ce{MoO3} morphologies: nanobelts and towers. We further demonstrated the application of as-synthesized \ce{MoO3} nanomaterials in electrochromic devices.  In chapter 4 we discuss the growth of \gls{tmdc} and associated heterostructures. We synthesized \ce{WO3}-\ce{WS2} core-shell \gls{nw} and inspected the growth of \gls{fl} \ce{WS2}. Chapter 5 will conclude with an overall summary.

\section{Nanomaterials for Energy Applications}

\section{Crystal Structures and Electronic Properties}

Solid and orderliness.

Two theories arise to describe the outer shell electrons and to correlate the structure and physical properties: \gls{cft} and band theory.\cite{Goodenough1971} \gls{cft} assumes weak interaction between neighboring atoms and localization of electron towards parent atom, whereas band theory assumes that electron is shared equally by all nuclei and therefore a many-electron problems follows. Description of a single electron in periodic potential fail to treat the electron correlations adequately, as the interaction between atoms becomes weaker.For transition metals, $s$ and $p$ electrons are well described by a collective-electron model, while the 4f or 5f electrons are tightly bound to nuclei and screened from the neighboring atoms by 5s, 5p or 6s, 6p core electrons, hence it matches well with a localized-electron model. d electrons show intermediate character.

\section{Growth Apparatus and Characterization Methods}
\subsection{CVD System}

Nucleation is a process of generating a new phase from a metastable old phase, where the Gibbs energy per molecule of the bulk of the emerging new phase is less than that of the old phase.

  General CVD knowledge, substrate preparation, and\cite{MichealK.Zuraw2003}

\subsection{Measurement}
sample/specimen preparation, data processing,

%\printbibliography  %  comment out when assembling

>>>>

\chapter{introduction}

\section{Background and Motivation: Nanomaterials for Energy Applications}

@@

Energy saving and harvesting.

\subsection{Electrochromism for Energy Saving}

coloration efficiency, the doping amount,

\subsection{Photocatalysis for Energy Harvesting}

\subsection{Advantage of Nano-engineering}

@@

The materials studied in this work/dissertation are tungsten oxides (\ce{WO3}), molybdenum oxides (\ce{MoO3}),and their chalcogenide counterparts (\ce{WS2} and \ce{MoS2}).

This dissertation work primarily focuses on growth and characterization, and will only present some preliminary tests on device and applications. Experimental tools for growth and characterization will be introduced in Chapter 2. Chapter 3 will be devoted to tungsten oxides (\ce{WO3}) and sodium tungsten oxides (\ce{Na5W14O44}) nanowires, where the role of sodium compounds in metallic tungsten precursors are thoroughly investigated. Chapter 4 will turn to molybdenum oxides (\ce{MoO3}) growth using alkaline metal compounds as catalysts. In Chapter 5, the growth of \gls{tmdc} and heterostructures will be discussed. Emphasis will be placed on the characterization of individual \ce{WO3}-\ce{WS2} core-shell \gls{nw}. The dissertation is then concluded with a summary and future work.

We have synthesized \gls{tmo} and \gls{tmdc} at nanoscale, measured their crystalline structures and optical properties and demonstrated some devices assembled using as-synthesized nanomaterials. We aim to illustrate that by nanoengineering these \gls{tmo} and \gls{tmdc}, enhanced performances over their bulk states could be expected and new properties will arise. In the remaining sections of this chapter, we will discuss some general perspectives of nanomaterials, the growth apparatus and characterization methods that apply to all experiments done in this work. Then chapter 2 will focus on growth of \ce{WO3} and its derivative. We employed thermal \gls{cvd} to synthesize \ce{WO3} \gls{nw}, and we investigated the role of impurity in tungsten metallic powders, during which we observed a new state of sodium tungsten oxides: \ce{Na5W14O44} nanowires. We also found a method to potentially obtain large yield of \ce{WO3} \gls{nw}. Chapter 3 will concentrate on \ce{MoO3}. We explored two different growth mechanism of \ce{MoO3}:\gls{vs} and \gls{vls}. We discovered that alkaline oxides can be used as catalyst to grow two distinct \ce{MoO3} morphologies: nanobelts and towers. We further demonstrated the application of as-synthesized \ce{MoO3} nanomaterials in electrochromic devices.  In chapter 4 we discuss  We synthesized  and inspected the growth of \gls{fl} \ce{WS2}. Chapter 5 will conclude with an overall summary.
